`flippant` --- An `R` package for the automated analysis of fluorescence--based

### 2016-12-22 inst/manuscript/manuscript.rmd
Unify title casing of section headers;

# Declarations {-}
## Ethics approval and consent to participate {-}
Not applicable.

## Consent to publish {-}
Not applicable.

## Availability of data and materials {-}
The `R` package `flippant` provides in an integrated manner and accessible
from within `R` all functionality as well as data presented here along with
extensive additional documentation and example code.

@@

## Competing interests {-}
The authors declare that they have no competing interests.

@@

## Authors' contributions {-}
R.J.C and J.G. wrote the code, B.P., M.A.G. and A.K.M. guided the implementation
and edited the manuscript, which J.G. wrote. B.P. provided the exemplary assay
data. A.K.M. and J.G. supervised the work.

@@

# Figure legends {-}
```{r figure1-creation, echo=FALSE, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** See text for command and details."}
# Plot spectral traces (Figure 1)
figure1_plot <- scramblase_assay_traces(
  template_file,
  time_max_sec = 350)
grid::rectGrob(
    width = grid::unit(0.1, "mm"),
    height = grid::unit(0.1, "mm")) %>%
  grid::grid.draw()
```

>>>>

# Declarations {-}
## Ethics Approval and Consent to Participate {-}
Not applicable.

## Consent to Publish {-}
Not applicable.

## Availability of Data and Materials {-}
The `R` package `flippant` provides in an integrated manner and accessible
from within `R` all functionality as well as data presented here along with
extensive additional documentation and example code.

@@

## Competing Interests {-}
The authors declare that they have no competing interests.

@@

## Authors' Contributions {-}
R.J.C and J.G. wrote the code, B.P., M.A.G. and A.K.M. guided the implementation
and edited the manuscript, which J.G. wrote. B.P. provided the exemplary assay
data. A.K.M. and J.G. supervised the work.

@@

# Figure Legends {-}
```{r figure1-creation, echo=FALSE, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** See text for command and details."}
# Plot spectral traces (Figure 1)
figure1_plot <- scramblase_assay_traces(
  template_file,
  time_max_sec = 350)
grid::rectGrob(
    width = grid::unit(0.1, "mm"),
    height = grid::unit(0.1, "mm")) %>%
  grid::grid.draw()
```
